Rule Synthesis for Rule-based Intrusion Detectors

### 2020-05-18 paper/paper.tex
pass on section 3 (halfway through)

Figure~\ref{fig:pingscan-example} \rui{any reason for the bolds?} shows a Suricata rule that captures
Ping Scan, as documented on NMAP~\cite{netmap}, a network security
auditing tool. The essential options to capture the attack are in
bold---the option \CodeIn{dsize: 0} indicates that the packet has no
bytes in the payload and the option \CodeIn{itype: 8} indicates that
the packet to be captured are ICMP Echo requests.

In the following, we briefly show how \tname{} synthesizes rules for
this attack. In short, \tname{} takes one or more examples of an
attack---in the form of network messages---and produces rules to
capture that attack. Considering the rule for the Ping Scan attack,
whose example was reproduced with NMAP, \tname{} leaves the action of
the corresponding rule constant (as \CodeIn{alert}) and infers the
header by checking the protocol of the input messages. For example, in
this case, \tname{} sets the header to \CodeIn{icmp any any -> any
  any}, indicating that the rule applies to \CodeIn{icmp} messages and
the most general flow description, \ie{}, it instructs the \nids\ to
analyze the icmp traffic flowing from/to any address and port.  The
rationale for this decision is that the choice of these parameters are
domain-specific and subject to change by the system administrator.

>>>>

Figure~\ref{fig:pingscan-example} shows a Suricata rule that captures
Ping Scan, as documented on NMAP~\cite{netmap}, a network security
auditing tool. The essential options to capture the attack are in
bold---the option \CodeIn{dsize: 0} indicates that the packet has no
bytes in the payload and the option \CodeIn{itype: 8} indicates that
the packet to be captured are ICMP Echo requests.

%---in the form of network messages---
% one or more examples of an attack
%, indicating that the rule applies to \CodeIn{icmp}messages

In the following, we show how \tname{} synthesizes rules for this
attack. \tname{} takes on input benign and malicious traffic and
produces on output rules to capture only the malicious
traffic. Considering the Ping Scan attack, \tname{} replays the
attack---with NMAP, in this case---and monitors the traffic.  It
infers the header by checking the protocol of the input messages. In
this case, \tname{} sets the header to \CodeIn{icmp any any -> any
  any}. It uses the most general flow description instructing the
\nids\ to analyze the icmp traffic flowing from/to any address and
port.  The rationale is that the choice of these parameters are
domain-specific and subject to change by the sys admins. Likewise,
\tname{} leaves the action of the corresponding rule constant, as
\CodeIn{alert}.

\Mar{--------------------- I am here...}
